### 2015-08-26 docs/article.tex
plan

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{IEEEtran}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

%\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
    The TransHumUs project for the French Pavilion \\ at La Biennale di Venezia 2015
}

%\author{Albert Author$^{1}$ and Bernard D. Researcher$^{2}$% <-this % stops a space
%\thanks{*This work was not supported by any organization}% <-this % stops a space
%\thanks{$^{1}$Albert Author is with Faculty of Electrical Engineering, Mathematics and Computer Science,
        %University of Twente, 7500 AE Enschede, The Netherlands
        %{\tt\small albert.author@papercept.net}}%
%\thanks{$^{2}$Bernard D. Researcheris with the Department of Electrical Engineering, Wright State University,
        %Dayton, OH 45435, USA
        %{\tt\small b.d.researcher@ieee.org}}%
%}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

    TODO

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{When robotics meets art}
\subsection{The transHumUs project of Céleste Boursier-Mougenot}
vue d’artiste
C/C institut français en anglais
\subsection{The robotics interpretation}
interpretation → discours sur le mouvement

\section{The robotic project}
\subsection{Specifications}
(en relation avec l’artiste)

* feedback sur métabolisme
* arbre de 3t
* holonomie
* silence
* lenteur
* couverture spatiale
* coordination

\subsection{Technical solutions}
* sondes Granier
* AGV tri-tourelles
* localisation absolue

\subsection{Architecture for the generation of motion}
* Présentation générale (scéma octogone avec le CIR)
* Schéma bloc
* captures d’écran du simulateur

\section{Implementation}
Photos

* sondes granier
* AGV désossé
* photo de pose des balises dans l’arbre
* arbre en acheminement

déroulement du projet
jusqu’à l’inauguration de la ministre

%$$
%\alpha + \beta = \chi \eqno{(1)}
%$$

   %\begin{figure}[thpb]
      %\centering
      %\framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
%}}
      %%\includegraphics[scale=1.0]{figurefile}
      %\caption{Inductance of oscillation winding on amorphous
       %magnetic core versus DC bias magnetic field}
      %\label{figurelabel}
   %\end{figure}

\section{Conclusion}

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.
\section*{APPENDIX}
\section*{ACKNOWLEDGMENT}
References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.
%\begin{thebibliography}{99}
%\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
%\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
%\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
%\bibitem{c4} B. Smith, ÒAn approach to graphs of linear forms (Unpublished work style),Ó unpublished.
%\bibitem{c5} E. H. Miller, ÒA note on reflector arrays (Periodical styleÑAccepted for publication),Ó IEEE Trans. Antennas Propagat., to be publised.
%\bibitem{c6} J. Wang, ÒFundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),Ó IEEE J. Quantum Electron., submitted for publication.
%\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
%\bibitem{c8} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ÒElectron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style),Ó IEEE Transl. J. Magn.Jpn., vol. 2, Aug. 1987, pp. 740Ð741 [Dig. 9th Annu. Conf. Magnetics Japan, 1982, p. 301].
%\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
%\bibitem{c10} J. U. Duncombe, ÒInfrared navigationÑPart I: An assessment of feasibility (Periodical style),Ó IEEE Trans. Electron Devices, vol. ED-11, pp. 34Ð39, Jan. 1959.
%\bibitem{c11} S. Chen, B. Mulgrew, and P. M. Grant, ÒA clustering technique for digital communications channel equalization using radial basis function networks,Ó IEEE Trans. Neural Networks, vol. 4, pp. 570Ð578, July 1993.
%\bibitem{c12} R. W. Lucky, ÒAutomatic equalization for digital communication,Ó Bell Syst. Tech. J., vol. 44, no. 4, pp. 547Ð588, Apr. 1965.
%\bibitem{c13} S. P. Bingulac, ÒOn the compatibility of adaptive controllers (Published Conference Proceedings style),Ó in Proc. 4th Annu. Allerton Conf. Circuits and Systems Theory, New York, 1994, pp. 8Ð16.
%\bibitem{c14} G. R. Faulhaber, ÒDesign of service systems with priority reservation,Ó in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3Ð8.
%\bibitem{c15} W. D. Doyle, ÒMagnetization reversal in films with biaxial anisotropy,Ó in 1987 Proc. INTERMAG Conf., pp. 2.2-1Ð2.2-6.
%\bibitem{c16} G. W. Juette and L. E. Zeffanella, ÒRadio noise currents n short sections on bundle conductors (Presented Conference Paper style),Ó presented at the IEEE Summer power Meeting, Dallas, TX, June 22Ð27, 1990, Paper 90 SM 690-0 PWRS.
%\bibitem{c17} J. G. Kreifeldt, ÒAn analysis of surface-detected EMG as an amplitude-modulated noise,Ó presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
%\bibitem{c18} J. Williams, ÒNarrow-band analyzer (Thesis or Dissertation style),Ó Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
%\bibitem{c19} N. Kawasaki, ÒParametric study of thermal and chemical nonequilibrium nozzle flow,Ó M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
%\bibitem{c20} J. P. Wilkinson, ÒNonlinear resonant circuit devices (Patent style),Ó U.S. Patent 3 624 12, July 16, 1990. 
%\end{thebibliography}
\end{document}

### 2015-08-26 docs/article.tex
ça commence douuucement

@@
 % The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
+\usepackage{graphics} % for pdf, bitmapped graphics files
+\usepackage{epsfig} % for postscript graphics files
+\usepackage{mathptmx} % assumes new font selection scheme installed
+\usepackage{times} % assumes new font selection scheme installed
+\usepackage{amsmath} % assumes amsmath package installed
+\usepackage{amssymb}  % assumes amsmath package installed
 
@@
 \begin{abstract}
-
-    TODO
-
 \end{abstract}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{The transHumUs project of Céleste Boursier-Mougenot}
-vue d’artiste
+
+\begin{figure}[thpb]
+    \centering
+    \includegraphics[width=\linewidth]{img/vue_artiste.jpg}
+    \caption{Artist's Impression}
+    \label{artists_impression}
+\end{figure}
+
 C/C institut français en anglais
+
 \subsection{The robotics interpretation}
+
 interpretation → discours sur le mouvement
@@
 \subsection{Specifications}
+
 (en relation avec l’artiste)
 
-* feedback sur métabolisme
-* arbre de 3t
-* holonomie
-* silence
-* lenteur
-* couverture spatiale
-* coordination
+\begin{itemize}
+    \item feedback sur métabolisme
+    \item arbre de 3t
+    \item holonomie
+    \item silence
+    \item lenteur
+    \item couverture spatiale
+    \item coordination
+\end{itemize}
 
 \subsection{Technical solutions}
-* sondes Granier
-* AGV tri-tourelles
-* localisation absolue
+
+\begin{itemize}
+    \item sondes Granier
+    \item AGV tri-tourelles
+    \item localisation absolue
+\end{itemize}
 
 \subsection{Architecture for the generation of motion}
-* Présentation générale (scéma octogone avec le CIR)
-* Schéma bloc
-* captures d’écran du simulateur
+
+\begin{itemize}
+    \item Présentation générale (schéma octogone avec le CIR)
+    \item Schéma bloc
+    \item captures d’écran du simulateur
+\end{itemize}
 
@@
 
-* sondes granier
-* AGV désossé
-* photo de pose des balises dans l’arbre
-* arbre en acheminement
+\begin{itemize}
+    \item sondes granier
+    \item AGV désossé
+    \item photo de pose des balises dans l’arbre
+    \item arbre en acheminement
+\end{itemize}
 
@@
 %$$
-
-   %\begin{figure}[thpb]
-      %\centering
-      %\framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
-%}}
-      %%\includegraphics[scale=1.0]{figurefile}
-      %\caption{Inductance of oscillation winding on amorphous
-       %magnetic core versus DC bias magnetic field}
-      %\label{figurelabel}
-   %\end{figure}
 
@@
 \section*{ACKNOWLEDGMENT}
-References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.
+%References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.
 %\begin{thebibliography}{99}

### 2015-08-27 trajectoires/partout.py
unsafe_way & check dist_path

@@ -9,6 +9,7 @@ from numpy import array, where, zeros
 
 from ..settings import BORDS, GRID_COEF, Hote
 from ..utils.dist_angles import dist_angle
+from ..utils.dist_path import dist_path
 from ..utils.no_overlap import no_overlap
 from ..utils.point_in_polygon import wn_pn_poly
 from ..utils.stay_in_poly import stay_in_poly
@@ -79,7 +80,7 @@ class TrajectoirePartout(TrajectoireDestination):
         while xd == yd == -1:
             xd, yd = self.find_dest_other(hote) if state == 0 else self.find_dest_extr(hote, state)
             xd, yd = xd / GRID_COEF * (-1 if hote == Hote.moro else 1), yd / GRID_COEF
-            if inside and (not stay_in_poly((x, y), (xd, yd), BORDS[hote]) or self.collision(hote, x, y, xd, yd)):
+            if inside and self.unsafe_way(x, y, xd, yd, hote):
                 failcount += 1
                 if failcount > 5:
                     state += 1
@@ -92,6 +93,10 @@ class TrajectoirePartout(TrajectoireDestination):
                 xd = yd = -1
         self.data[hote].update(state=state, destination=(xd, yd), dest_next=False, dest_prev=False)
         self.invert_direction(**self.data[hote])
+
+    def unsafe_way(self, x, y, xd, yd, hote):
+        marge = 0 if dist_path(BORDS[hote], (x, y)) < 1 else 0.5
+        return not stay_in_poly((x, y), (xd, yd), BORDS[hote], marge=marge) or self.collision(hote, x, y, xd, yd)
 
     def invert_direction(self, hote, t, x, y, a, w, destination, inverse_rot, **kwargs):
         """ inverse la direction et la rotation si la nouvelle destination est à plus de 2π/3 """

### 2015-08-28 docs/article.tex
dessin

@@
 %\overrideIEEEmargins                                      % Needed to meet printer requirements.
+
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+
+\usepackage{tikz}
+\usetikzlibrary{calc,patterns,angles,quotes,shapes}
 
@@
 \begin{abstract}
+    TODO
 \end{abstract}
@@
 
-C/C institut français en anglais
+For the 56th edition of the Venice Biennale International Contemporary Art Exhibit, Céleste Boursier-Mougenot composed a poetic work evoking the follies of 18th-century romantic parks, while revealing its political dimension.
+
+With rêvolutions by artist Céleste Boursier-Mougenot, accompanied by the exhibit’s Curator, Emma Lavigne, the French Pavilion of the Venice Biennale has been transformed into an organic, dreamlike isle.
+
+Under the glass roof, with the Pavilion’s flight and tree-lined lanes of the Giardini, Céleste Boursier-Mougenot has rolled out the choreography of three mobile trees moving according to their metabolism, the varying flow of their sap and their sensitivity when going from shadow to light.
 
@@
 
-interpretation → discours sur le mouvement
+TODO interpretation → discours sur le mouvement
 
@@
 
-(en relation avec l’artiste)
+Acording to the artist's wishes, we established the initial specifications for the piece of art, in order to find the right industrial partners:
 
 \begin{itemize}
-    \item feedback sur métabolisme
-    \item arbre de 3t
-    \item holonomie
-    \item silence
-    \item lenteur
-    \item couverture spatiale
-    \item coordination
+    \item The artwork will be composed by three trees of approximately 4 to 5 meters high and 3 tons;
+    \item They will move in accordance with some feedback from their metabolism;
+    \item The movement will be holonomic in a plane;
+    \item The trees will have to move silently;
+    \item The motion must be really slow, hardly perceptible (between 0 and 1 meter per minute);
+    \item The trajectory shall cover as much as possible the available space;
+    \item Several trees will have to coordinate themselves in the same area;
+    \item The wheelbase must be able to roll on soft floors (mud and gravels) as well as on hard ones (concrete).
 \end{itemize}
@@
 
+\paragraph{Sapflow sensors} have been selected by biology researchers as they can provide a reliable signal correlated with the tree's metabolism.
+
+\paragraph{Automatic Guided Vehicles} (AGV) with three directable wheels should comply with the admissible mechanical load on the concrete and provide an overall holonomic motion possibility.
+
+\paragraph{Absolute geolocation} that works well indoor and outdoor, including on bumpy areas, at an affordable price is hard to find, but exists.
+
+\subsection{Architecture for the generation of motion}
+
+As the artist wants an holonomic planar motion, in the most basic form, we need input 3 variables.
+The artist also wish that the trees behave in a similar manner in whatever direction it goes, so we choose a polar coordinate system concentric with the AGV: $(v, \theta, \omega)$, where:
+
 \begin{itemize}
-    \item sondes Granier
-    \item AGV tri-tourelles
-    \item localisation absolue
+    \item $\theta \in [0, 2\pi[$ is the direction of the center of the AGV;
+    \item $v \in [-1, 1]$ is its linear velocity along the direction $\theta$;
+    \item $\omega \in [-1, 1]$ is its angular velocity.
 \end{itemize}
 
-\subsection{Architecture for the generation of motion}
+With this system, we can easily compute the output needed by the AGV, which consist of the orientation $\theta_i$ of each wheel and its traction velocity $v_i$:
+
+\begin{eqnarray*}
+    v_{xi} &=& v \cos(\theta)- \omega \sin(\alpha_i) \\
+    v_{yi} &=& v \sin(\theta)+ \omega \cos(\alpha_i) \\
+    v_i &=& \sqrt{v_{xi}^2 + v_{yi}^2} \\
+    \theta_i &=& \arctan(v_{yi}, v_{xi})
+\end{eqnarray*}
+
+\begin{figure}[thpb]
+    \centering
+    \begin{tikzpicture}
+        \coordinate (o) at (0,0);
+        \coordinate (v) at (0.5, {sqrt(3) / 2});
+        \coordinate (x) at ({-sqrt(2) / 2}, {-sqrt(2) / 2});
+        \coordinate (y) at ({+sqrt(2) / 2}, {-sqrt(2) / 2});
+        \coordinate (z) at (0, 1);
+        \draw (o) node [draw,thick,minimum size=4cm,name=O,regular polygon,regular polygon sides=8] {};
+        \draw (O) node [fill=green,circle,draw,inner sep=1pt] {};
+        \coordinate (a) at (O.side 2);
+        \coordinate (b) at (O.side 4);
+        \coordinate (c) at (O.side 7);
+        \coordinate (d) at (O.side 6);
+        \draw (a) node [fill=red,circle,draw,inner sep=1pt] {};
+        \draw (b) node [fill=red,circle,draw,inner sep=1pt] {};
+        \draw (c) node [fill=red,circle,draw,inner sep=1pt] {};
+        \draw [->, red] (o) -- (v) node [above] {$v$};
+        \draw [->, red] (a) -- ++(v) node [above] {$v$};
+        \draw [->, red] (b) -- ++(v) node [left] {$v$};
+        \draw [->, red] (c) -- ++(v) node [right] {$v$};
+        \draw [->, blue] (a) -- ++(x) node [left] {$\omega R_2$};
+        \draw [->, blue] (b) -- ++(y) node [pos=0.7, left] {$\omega R_3$};
+        \draw [->, blue] (c) -- ++(z) node [pos=0.5, left] {$\omega R_1$};
+        \draw [->] (a) -- ($ (a) + (v) + (x) $) node [left] {$v_2$};
+        \draw [->] (b) -- ($ (b) + (v) + (y) $) node [right] {$v_3$};
+        \draw [->] (c) -- ($ (c) + (v) + (z) $) node [above] {$v_1$};
+        \draw [dashed] ($ (a) + (v) $) -- ($ (a) + (v) + (x) $);
+        \draw [dashed] ($ (b) + (v) $) -- ($ (b) + (v) + (y) $);
+        \draw [dashed] ($ (c) + (v) $) -- ($ (c) + (v) + (z) $);
+        \draw [dashed] ($ (a) + (x) $) -- ($ (a) + (v) + (x) $);
+        \draw [dashed] ($ (b) + (y) $) -- ($ (b) + (v) + (y) $);
+        \draw [dashed] ($ (c) + (z) $) -- ($ (c) + (v) + (z) $);
+        \draw [blue] (o) -- (a) node [pos=0.5, above] {$R_2$};
+        \draw [blue] (o) -- (b) node [pos=0.5, below] {$R_3$};
+        \draw [blue] (o) -- (c) node [pos=0.5, below] {$R_1$};
+        \pic [black!60!green, draw, ->, "$\theta$", angle eccentricity=1.5] {angle = c--o--v};
+        \pic [blue, draw, ->, "$\omega$", angle eccentricity=1.1, angle radius=75] {angle = d--o--c};
+    \end{tikzpicture}
+    \caption{$(v_i, \theta_i)$ as a function of $(v, \theta, \omega)$}
+    \label{octogon}
+\end{figure}
 
@@
 \section{Implementation}
+
 Photos

### 2015-08-28 docs/article.tex
joliage

@@
     \begin{tikzpicture}
+        \draw [->] (-3, 0) -- (3, 0);
+        \draw [->] (0, -3) -- (0, 3);
         \coordinate (o) at (0,0);
         \coordinate (v) at (0.5, {sqrt(3) / 2});
-        \coordinate (x) at ({-sqrt(2) / 2}, {-sqrt(2) / 2});
-        \coordinate (y) at ({+sqrt(2) / 2}, {-sqrt(2) / 2});
-        \coordinate (z) at (0, 1);
+        \coordinate (x) at ({+sqrt(2) / 2}, {sqrt(2) / 2});
+        \coordinate (y) at ({-sqrt(2) / 2}, {sqrt(2) / 2});
+        \coordinate (z) at (0, -1);
         \draw (o) node [draw,thick,minimum size=4cm,name=O,regular polygon,regular polygon sides=8] {};
         \draw (O) node [fill=green,circle,draw,inner sep=1pt] {};
-        \coordinate (a) at (O.side 2);
-        \coordinate (b) at (O.side 4);
-        \coordinate (c) at (O.side 7);
-        \coordinate (d) at (O.side 6);
+        \coordinate (a) at (O.side 6);
+        \coordinate (b) at (O.side 8);
+        \coordinate (c) at (O.side 3);
+        \coordinate (d) at ($ (O.side 7) + (0, 0.5) $);
         \draw (a) node [fill=red,circle,draw,inner sep=1pt] {};
@@
         \draw (c) node [fill=red,circle,draw,inner sep=1pt] {};
-        \draw [->, red] (o) -- (v) node [above] {$v$};
-        \draw [->, red] (a) -- ++(v) node [above] {$v$};
-        \draw [->, red] (b) -- ++(v) node [left] {$v$};
-        \draw [->, red] (c) -- ++(v) node [right] {$v$};
-        \draw [->, blue] (a) -- ++(x) node [left] {$\omega R_2$};
-        \draw [->, blue] (b) -- ++(y) node [pos=0.7, left] {$\omega R_3$};
-        \draw [->, blue] (c) -- ++(z) node [pos=0.5, left] {$\omega R_1$};
-        \draw [->] (a) -- ($ (a) + (v) + (x) $) node [left] {$v_2$};
-        \draw [->] (b) -- ($ (b) + (v) + (y) $) node [right] {$v_3$};
-        \draw [->] (c) -- ($ (c) + (v) + (z) $) node [above] {$v_1$};
-        \draw [dashed] ($ (a) + (v) $) -- ($ (a) + (v) + (x) $);
-        \draw [dashed] ($ (b) + (v) $) -- ($ (b) + (v) + (y) $);
-        \draw [dashed] ($ (c) + (v) $) -- ($ (c) + (v) + (z) $);
-        \draw [dashed] ($ (a) + (x) $) -- ($ (a) + (v) + (x) $);
-        \draw [dashed] ($ (b) + (y) $) -- ($ (b) + (v) + (y) $);
-        \draw [dashed] ($ (c) + (z) $) -- ($ (c) + (v) + (z) $);
-        \draw [blue] (o) -- (a) node [pos=0.5, above] {$R_2$};
-        \draw [blue] (o) -- (b) node [pos=0.5, below] {$R_3$};
-        \draw [blue] (o) -- (c) node [pos=0.5, below] {$R_1$};
-        \pic [black!60!green, draw, ->, "$\theta$", angle eccentricity=1.5] {angle = c--o--v};
-        \pic [blue, draw, ->, "$\omega$", angle eccentricity=1.1, angle radius=75] {angle = d--o--c};
+        \draw [->, red] (o) -- (v) node [left] {$v$};
+        \draw [->, red] (a) -- ++(v) node [left] {$v$};
+        \draw [->, red] (b) -- ++(v) node [right] {$v$};
+        \draw [->, red] (c) -- ++(v) node [left] {$v$};
+        \draw [->, blue] (a) -- ++(x) node [right] {$\omega R_1$};
+        \draw [->, blue] (b) -- ++(y) node [left] {$\omega R_2$};
+        \draw [->, blue] (c) -- ++(z) node [left] {$\omega R_3$};
+        \draw [->] (a) -- ($ (a) + (v) + (x) $) node [left] {$v_1$};
+        \draw [->] (b) -- ($ (b) + (v) + (y) $) node [left] {$v_2$};
+        \draw [->] (c) -- ($ (c) + (v) + (z) $) node [below] {$v_3$};
+        \draw [blue, dashed] ($ (a) + (v) $) -- ($ (a) + (v) + (x) $);
+        \draw [blue, dashed] ($ (b) + (v) $) -- ($ (b) + (v) + (y) $);
+        \draw [blue, dashed] ($ (c) + (v) $) -- ($ (c) + (v) + (z) $);
+        \draw [red, dashed] ($ (a) + (x) $) -- ($ (a) + (v) + (x) $);
+        \draw [red, dashed] ($ (b) + (y) $) -- ($ (b) + (v) + (y) $);
+        \draw [red, dashed] ($ (c) + (z) $) -- ($ (c) + (v) + (z) $);
+        \draw [blue] (o) -- (a) node [pos=0.5, above] {$R_1$};
+        \draw [blue] (o) -- (b) node [pos=0.7, below] {$R_2$};
+        \draw [blue] (o) -- (c) node [pos=0.5, above] {$R_3$};
+        \pic [black!60!green, draw, ->, "$\theta$", angle eccentricity=1.5] {angle = d--o--v};
+        \pic [blue, draw, ->, "$\omega$", angle eccentricity=1.1, angle radius=75] {angle = d--o--b};
     \end{tikzpicture}

### 2015-08-31 docs/article.tex
fig_ok

@@
     \centering
+
     \begin{tikzpicture}
@@
         \draw [->] (0, -3) -- (0, 3);
-        \coordinate (o) at (0,0);
+        \coordinate (o) at (0, 0);
         \coordinate (v) at (0.5, {sqrt(3) / 2});
@@
         \coordinate (z) at (0, -1);
-        \draw (o) node [draw,thick,minimum size=4cm,name=O,regular polygon,regular polygon sides=8] {};
-        \draw (O) node [fill=green,circle,draw,inner sep=1pt] {};
+        \draw (o) node [draw, thick, minimum size=4cm, name=O, regular polygon, regular polygon sides=8] {};
+        \draw (O) node [fill=green, circle, draw, inner sep=1pt] {};
         \coordinate (a) at (O.side 6);
@@
         \coordinate (c) at (O.side 3);
-        \coordinate (d) at ($ (O.side 7) + (0, 0.5) $);
-        \draw (a) node [fill=red,circle,draw,inner sep=1pt] {};
-        \draw (b) node [fill=red,circle,draw,inner sep=1pt] {};
-        \draw (c) node [fill=red,circle,draw,inner sep=1pt] {};
+        \coordinate (d) at (O.side 7);
+        \coordinate (e) at ($ (d) + (0, 0.5) $);
+        \coordinate (f) at ($ (a) + (1, 0) $);
+        \coordinate (g) at ($ (b) + (1, 0) $);
+        \coordinate (h) at ($ (c) + (1, 0) $);
+        \coordinate (i) at ($ (a) + (v) + (x) $);
+        \coordinate (j) at ($ (b) + (v) + (y) $);
+        \coordinate (k) at ($ (c) + (v) + (z) $);
+        \draw (a) node [fill=red, circle, draw, inner sep=1pt] {};
+        \draw (b) node [fill=red, circle, draw, inner sep=1pt] {};
+        \draw (c) node [fill=red, circle, draw, inner sep=1pt] {};
         \draw [->, red] (o) -- (v) node [left] {$v$};
@@
         \draw [->, blue] (c) -- ++(z) node [left] {$\omega R_3$};
-        \draw [->] (a) -- ($ (a) + (v) + (x) $) node [left] {$v_1$};
-        \draw [->] (b) -- ($ (b) + (v) + (y) $) node [left] {$v_2$};
-        \draw [->] (c) -- ($ (c) + (v) + (z) $) node [below] {$v_3$};
-        \draw [blue, dashed] ($ (a) + (v) $) -- ($ (a) + (v) + (x) $);
-        \draw [blue, dashed] ($ (b) + (v) $) -- ($ (b) + (v) + (y) $);
-        \draw [blue, dashed] ($ (c) + (v) $) -- ($ (c) + (v) + (z) $);
-        \draw [red, dashed] ($ (a) + (x) $) -- ($ (a) + (v) + (x) $);
-        \draw [red, dashed] ($ (b) + (y) $) -- ($ (b) + (v) + (y) $);
-        \draw [red, dashed] ($ (c) + (z) $) -- ($ (c) + (v) + (z) $);
+        \draw [->] (a) -- (i) node [left] {$v_1$};
+        \draw [->] (b) -- (j) node [left] {$v_2$};
+        \draw [->] (c) -- (k) node [below] {$v_3$};
+        \draw [blue, dashed] ($ (a) + (v) $) -- (i);
+        \draw [blue, dashed] ($ (b) + (v) $) -- (j);
+        \draw [blue, dashed] ($ (c) + (v) $) -- (k);
+        \draw [red, dashed] ($ (a) + (x) $) -- (i);
+        \draw [red, dashed] ($ (b) + (y) $) -- (j);
+        \draw [red, dashed] ($ (c) + (z) $) -- (k);
         \draw [blue] (o) -- (a) node [pos=0.5, above] {$R_1$};
@@
         \pic [black!60!green, draw, ->, "$\theta$", angle eccentricity=1.5] {angle = d--o--v};
-        \pic [blue, draw, ->, "$\omega$", angle eccentricity=1.1, angle radius=75] {angle = d--o--b};
+        \pic [blue, draw, ->, "$\omega$", angle eccentricity=1.1, angle radius=80] {angle = e--o--b};
+        \pic [draw, ->, "$\theta_1$", angle radius=20, angle eccentricity=1.3] {angle = f--a--i};
+        \pic [draw, ->, "$\theta_2$", angle radius=10, angle eccentricity=1.5] {angle = g--b--j};
+        \pic [draw, ->, "$\theta_3$", angle radius=5, angle eccentricity=2] {angle = h--c--k};
     \end{tikzpicture}
+
     \caption{$(v_i, \theta_i)$ as a function of $(v, \theta, \omega)$}

### 2015-08-31 docs/article.tex
two_figs

@@
 \usetikzlibrary{calc,patterns,angles,quotes,shapes}
+\usepackage{subcaption}
 
@@
 
+            \begin{subfigure}{.5\textwidth}
+                \centering
                 \begin{tikzpicture}
-        \draw [->] (-3, 0) -- (3, 0);
-        \draw [->] (0, -3) -- (0, 3);
+                    \draw [->] (-2, 0) -- (3, 0);
+                    \draw [->] (0, -2) -- (0, 3);
                     \coordinate (o) at (0, 0);
@@
                     \draw (c) node [fill=red, circle, draw, inner sep=1pt] {};
-        \draw [->, red] (o) -- (v) node [left] {$v$};
-        \draw [->, red] (a) -- ++(v) node [left] {$v$};
-        \draw [->, red] (b) -- ++(v) node [right] {$v$};
-        \draw [->, red] (c) -- ++(v) node [left] {$v$};
-        \draw [->, blue] (a) -- ++(x) node [right] {$\omega R_1$};
-        \draw [->, blue] (b) -- ++(y) node [left] {$\omega R_2$};
-        \draw [->, blue] (c) -- ++(z) node [left] {$\omega R_3$};
-        \draw [->] (a) -- (i) node [left] {$v_1$};
-        \draw [->] (b) -- (j) node [left] {$v_2$};
-        \draw [->] (c) -- (k) node [below] {$v_3$};
+                    \draw [->, -latex, red] (o) -- (v) node [above] {$v$};
+                    \pic [blue, draw, ->, -latex, "$\omega$", angle eccentricity=1.1, angle radius=80] {angle = e--o--b};
+                    \draw [->, -latex] (a) -- (i) node [above] {$v_1$};
+                    \draw [->, -latex] (b) -- (j) node [above] {$v_2$};
+                    \draw [->, -latex] (c) -- (k) node [right] {$v_3$};
+
+                    \pic [black!60!green, draw, ->, -latex, "$\theta$", angle eccentricity=1.5] {angle = d--o--v};
+                    \pic [draw, ->, -latex, "$\theta_1$", angle radius=30, angle eccentricity=1.2] {angle = f--a--i};
+                    \pic [draw, ->, -latex, "$\theta_2$", angle radius=15, angle eccentricity=1.5] {angle = g--b--j};
+                    \pic [draw, ->, -latex, "$\theta_3$", angle radius=8, angle eccentricity=2] {angle = h--c--k};
+                \end{tikzpicture}
+                \caption{From $(v, \theta, \omega)$ to $(v_i, \theta_i)$}
+            \end{subfigure}
+
+            \begin{subfigure}{.5\textwidth}
+                \centering
+                \begin{tikzpicture}
+                    \draw [->] (-2, 0) -- (3, 0);
+                    \draw [->] (0, -2) -- (0, 3);
+                    \coordinate (o) at (0, 0);
+                    \coordinate (v) at (0.5, {sqrt(3) / 2});
+                    \coordinate (x) at ({+sqrt(2) / 2}, {sqrt(2) / 2});
+                    \coordinate (y) at ({-sqrt(2) / 2}, {sqrt(2) / 2});
+                    \coordinate (z) at (0, -1);
+                    \draw (o) node [draw, thick, minimum size=4cm, name=O, regular polygon, regular polygon sides=8] {};
+                    \draw (O) node [fill=green, circle, draw, inner sep=1pt] {};
+                    \coordinate (a) at (O.side 6);
+                    \coordinate (b) at (O.side 8);
+                    \coordinate (c) at (O.side 3);
+                    \coordinate (d) at (O.side 7);
+                    \coordinate (e) at ($ (d) + (0, 0.5) $);
+                    \coordinate (f) at ($ (a) + (1, 0) $);
+                    \coordinate (g) at ($ (b) + (1, 0) $);
+                    \coordinate (h) at ($ (c) + (1, 0) $);
+                    \coordinate (i) at ($ (a) + (v) + (x) $);
+                    \coordinate (j) at ($ (b) + (v) + (y) $);
+                    \coordinate (k) at ($ (c) + (v) + (z) $);
+                    \draw (a) node [fill=red, circle, draw, inner sep=1pt] {};
+                    \draw (b) node [fill=red, circle, draw, inner sep=1pt] {};
+                    \draw (c) node [fill=red, circle, draw, inner sep=1pt] {};
+                    \draw [->, -latex, red] (o) -- (v) node [above] {$v$};
+                    \pic [blue, draw, ->, -latex, "$\omega$", angle eccentricity=1.1, angle radius=80] {angle = e--o--b};
+                    \draw [->, -latex] (a) -- (i) node [above] {$v_1$};
+                    \draw [->, -latex] (b) -- (j) node [above] {$v_2$};
+                    \draw [->, -latex] (c) -- (k) node [right] {$v_3$};
+
+                    \draw [blue] (o) -- (a) node [pos=0.5, right] {$R_1$};
+                    \draw [blue] (o) -- (b) node [pos=0.5, right] {$R_2$};
+                    \draw [blue] (o) -- (c) node [pos=0.5, above] {$R_3$};
+                    \draw [->, -latex, red] (a) -- ++(v) node [left] {$v$};
+                    \draw [->, -latex, red] (b) -- ++(v) node [above] {$v$};
+                    \draw [->, -latex, red] (c) -- ++(v) node [above] {$v$};
+                    \draw [->, -latex, blue] (a) -- ++(x) node [right] {$\omega R_1$};
+                    \draw [->, -latex, blue] (b) -- ++(y) node [above] {$\omega R_2$};
+                    \draw [->, -latex, blue] (c) -- ++(z) node [below] {$\omega R_3$};
                     \draw [blue, dashed] ($ (a) + (v) $) -- (i);
@@
                     \draw [red, dashed] ($ (c) + (z) $) -- (k);
-        \draw [blue] (o) -- (a) node [pos=0.5, above] {$R_1$};
-        \draw [blue] (o) -- (b) node [pos=0.7, below] {$R_2$};
-        \draw [blue] (o) -- (c) node [pos=0.5, above] {$R_3$};
-        \pic [black!60!green, draw, ->, "$\theta$", angle eccentricity=1.5] {angle = d--o--v};
-        \pic [blue, draw, ->, "$\omega$", angle eccentricity=1.1, angle radius=80] {angle = e--o--b};
-        \pic [draw, ->, "$\theta_1$", angle radius=20, angle eccentricity=1.3] {angle = f--a--i};
-        \pic [draw, ->, "$\theta_2$", angle radius=10, angle eccentricity=1.5] {angle = g--b--j};
-        \pic [draw, ->, "$\theta_3$", angle radius=5, angle eccentricity=2] {angle = h--c--k};
                 \end{tikzpicture}
+                \caption{Geometrical construction of $(v_i, \theta_i)$}
+            \end{subfigure}
 
@@
         %\begin{thebibliography}{99}
-%\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
+        %\bibitem{c1} G.
+O.
+Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed.
+vol.
+3, J.
+Peters, Ed.
+New York: McGraw-Hill, 1964, pp.
+15Ð64.
         %\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.

### 2015-08-31 docs/article.tex
auteurs

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
-
-\documentclass[letterpaper, 10 pt, conference]{IEEEtran}  % Comment this line out if you need a4paper
-
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
-
-\IEEEoverridecommandlockouts                              % This command is only needed if 
-% you want to use the \thanks command
-
-%\overrideIEEEmargins                                      % Needed to meet printer requirements.
+\documentclass[letterpaper, 10 pt, conference]{IEEEtran}
+%\documentclass[a4paper, 10pt, conference]{ieeeconf}
 
@@
 
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
+\usepackage{graphics}
+\usepackage{mathptmx}
+\usepackage{times}
+\usepackage{amsmath}
+\usepackage{amssymb}
 
-% The following packages can be found on http:\\www.ctan.org
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{times} % assumes new font selection scheme installed
-\usepackage{amsmath} % assumes amsmath package installed
-\usepackage{amssymb}  % assumes amsmath package installed
+\title{\LARGE \bf The TransHumUs project for the French Pavilion \\ at La Biennale di Venezia 2015}
 
-\title{\LARGE \bf
-    The TransHumUs project for the French Pavilion \\ at La Biennale di Venezia 2015
-}
-
-%\author{Albert Author$^{1}$ and Bernard D. Researcher$^{2}$% <-this % stops a space
-%\thanks{*This work was not supported by any organization}% <-this % stops a space
-%\thanks{$^{1}$Albert Author is with Faculty of Electrical Engineering, Mathematics and Computer Science,
-%University of Twente, 7500 AE Enschede, The Netherlands
-%{\tt\small albert.author@papercept.net}}%
-%\thanks{$^{2}$Bernard D. Researcheris with the Department of Electrical Engineering, Wright State University,
-%Dayton, OH 45435, USA
-%{\tt\small b.d.researcher@ieee.org}}%
-%}
+\author{Guilhem Saurel, Michel Taix and Jean-Paul Laumond}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
@@
 \end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{When robotics meets art}
@@
 
-        %$$
-        %\alpha + \beta = \chi \eqno{(1)}
-        %$$
-
         \section{Conclusion}
 
-        \addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-        % on the last page of the document manually. It shortens
-        % the textheight of the last page by a suitable amount.
-        % This command does not take effect until the next page
-        % so it should come on the page before the last. Make
-        % sure that you do not shorten the textheight too much.
         \section*{APPENDIX}
         \section*{ACKNOWLEDGMENT}
-        %References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.
-        %\begin{thebibliography}{99}
-        %\bibitem{c1} G.
-O.
-Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed.
-vol.
-3, J.
-Peters, Ed.
-New York: McGraw-Hill, 1964, pp.
-15Ð64.
-        %\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
-        %\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
-        %\bibitem{c4} B. Smith, ÒAn approach to graphs of linear forms (Unpublished work style),Ó unpublished.
-        %\bibitem{c5} E. H. Miller, ÒA note on reflector arrays (Periodical styleÑAccepted for publication),Ó IEEE Trans. Antennas Propagat., to be publised.
-        %\bibitem{c6} J. Wang, ÒFundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),Ó IEEE J. Quantum Electron., submitted for publication.
-        %\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
-        %\bibitem{c8} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ÒElectron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style),Ó IEEE Transl.
-J.
-Magn.Jpn., vol.
-2, Aug.
-1987, pp.
-740Ð741 [Dig.
-9th Annu.
-Conf.
-Magnetics Japan, 1982, p.
-301].
-        %\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
-        %\bibitem{c10} J. U. Duncombe, ÒInfrared navigationÑPart I: An assessment of feasibility (Periodical style),Ó IEEE Trans. Electron Devices, vol. ED-11, pp. 34Ð39, Jan. 1959.
-        %\bibitem{c11} S.
-Chen, B.
-Mulgrew, and P.
-M.
-Grant, ÒA clustering technique for digital communications channel equalization using radial basis function networks,Ó IEEE Trans.
-Neural Networks, vol.
-4, pp.
-570Ð578, July 1993.
-        %\bibitem{c12} R. W. Lucky, ÒAutomatic equalization for digital communication,Ó Bell Syst. Tech. J., vol. 44, no. 4, pp. 547Ð588, Apr. 1965.
-        %\bibitem{c13} S.
-P.
-Bingulac, ÒOn the compatibility of adaptive controllers (Published Conference Proceedings style),Ó in Proc.
-4th Annu.
-Allerton Conf.
-Circuits and Systems Theory, New York, 1994, pp.
-8Ð16.
-        %\bibitem{c14} G. R. Faulhaber, ÒDesign of service systems with priority reservation,Ó in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3Ð8.
-        %\bibitem{c15} W. D. Doyle, ÒMagnetization reversal in films with biaxial anisotropy,Ó in 1987 Proc. INTERMAG Conf., pp. 2.2-1Ð2.2-6.
-        %\bibitem{c16} G.
-W.
-Juette and L.
-E.
-Zeffanella, ÒRadio noise currents n short sections on bundle conductors (Presented Conference Paper style),Ó presented at the IEEE Summer power Meeting, Dallas, TX, June 22Ð27, 1990, Paper 90 SM 690-0 PWRS.
-        %\bibitem{c17} J. G. Kreifeldt, ÒAn analysis of surface-detected EMG as an amplitude-modulated noise,Ó presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
-        %\bibitem{c18} J. Williams, ÒNarrow-band analyzer (Thesis or Dissertation style),Ó Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
-        %\bibitem{c19} N. Kawasaki, ÒParametric study of thermal and chemical nonequilibrium nozzle flow,Ó M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
-        %\bibitem{c20} J. P. Wilkinson, ÒNonlinear resonant circuit devices (Patent style),Ó U.S. Patent 3 624 12, July 16, 1990. 
-        %\end{thebibliography}
+        \addtolength{\textheight}{-12cm}  % TODO
         \end{document}
